\setauthor{Antonio Peric}
\begin{spacing}{1}
    \chapter*{Abstract}
\end{spacing}
This thesis aims to modernize the training plan process at the LionFit gym.
\newline
The training data is currently recorded on printed paper.
\newline
This project involves developing a native app using Android Studio and Flutter to create a digital solution to provide management and monitoring of training plans.
\newline
The app replaces the old-fashioned paper training plan by reading the current training plan, created for the customer, from the database and clearly displaying it in the app with the latest training data.
\newline
The app also offers a way to keep track of the training by showing the user the exercises he needs to complete and a counter to keep track of the sets left.
\newline
These features make the entire training process more efficient, convenient and easier for gym customers.
\newpage
\setauthor{Antonio Peric}
\begin{spacing}{1}
    \chapter*{Zusammenfassung}
\end{spacing}
Diese Diplomarbeit zielt darauf ab, den Trainingsplanprozess im Fitnessstudio LionFit zu modernisieren. 
\newline
Derzeit werden die Trainingsdaten auf dem ausgedruckten PDF erfasst.
\newline
Das Projekt beinhaltet die Entwicklung einer nativen App mit Android Studio und Flutter, um eine digitale Lösung für 
die Verwaltung und Überwachung von Trainingsplänen zu bieten. 
\newline
Die App ersetzt den altmodischen Papier-Trainingsplan indem der aktuelle Trainingsplan des Kunden aus der Datenbank ausgelesen und übersichtlich mit den aktuellsten Trainingsdaten in der App anzeigt wird.
\newline 
Die App bietet auch eine To-Do Liste und einen Satzzähler, der es ermöglicht die Sätze der ausgewählten Übung zu zählen, um die Übungen abzuschließen.
\newline
Diese Funktionen gestalten den gesamten Trainingsprozess für Kunden des Fitnessstudios effizienter, bequemer und einfacher.

